DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-10-19 scnn.tex
small edit
small changes

\title{HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications}
% \title{Efficient Spherical ConvNet with Graph Convolutions for Cosmological Applications}
% \title{HealpixNet: Efficient spherical Convolutional Neural Network with graphs and HEALPix sampling for cosmological applications}
%\title{HealpixNet: Graph Convolutional Neural Network for efficient spherical convolutions on HEALPix sampling for cosmological applications}
% Graph Convolutional Networks for efficient spherical ???
% Efficient spherical ??? with GCNs and HEALPix sampling
% (Tomek) How about HealpixCNN? Or HealpixNet? Or HealNet?}
% spherical convolutions with graphs

@@

\author[SDSC]{Nathanaël Perraudin}
\author[EPFL]{Michaël Defferrard}
\author[ETHZ]{Tomasz Kacprzak}
\author[ETHZ]{Raphael Sgier(?)}

@@

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
	\item (TK) Check use of British vs American English. Check use of tense.
	\item (TK) Larger text on figure 2. I (MD) made it one column wide instead of two as it's more an illustration than a central figure to our exposition.
	\item (MD) Figure 4: speed for multiple lmax.
    \item (TK) check part sphere notebook and whole sphere
    \item (NP) Put Raphael in the dataset author.
	\item (NP \& MD) Move the git repository, rename the classes, check the links.
    \item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item (I think it is OK) (NP) Check the wording. Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
    \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly. MD: lmodern is better, but can we use it (w.r.t.\ journal policy)? If equations split out, we can try to arrange them. We should also check which font size we can / have to use.
\end{itemize}

>>>>

\title{DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications}
% \title{Efficient Spherical ConvNet with Graph Convolutions for Cosmological Applications}
% \title{HealpixNet: Efficient spherical Convolutional Neural Network with graphs and HEALPix sampling for cosmological applications}
%\title{HealpixNet: Graph Convolutional Neural Network for efficient spherical convolutions on HEALPix sampling for cosmological applications}
% Graph Convolutional Networks for efficient spherical ???
% Efficient spherical ??? with GCNs and HEALPix sampling
% (Tomek) How about HealpixCNN? Or HealpixNet? Or HealNet?}
% spherical convolutions with graphs

@@

\author[SDSC]{Nathanaël Perraudin}
\author[EPFL]{Michaël Defferrard}
\author[ETHZ]{Tomasz Kacprzak}
\author[ETHZ]{Raphael Sgier}

@@

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
	\nati{No answer from the people. Let us go for DeepSphere. Graphsphere???}
	\item (TK) Check use of British vs American English. Check use of tense.
	\item (MD) Figure 4: speed for multiple lmax. Not doing it.
    \item (TK) check part sphere notebook and whole sphere
	\item (NP \& MD) Move the git repository, rename the classes, check the links.
    \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly. MD: lmodern is better, but can we use it (w.r.t.\ journal policy)? If equations split out, we can try to arrange them. We should also check which font size we can / have to use.
\end{itemize}
